### 2014-10-15 RelatedWork.tex
small edits

There has been a lot of work in providing frameworks for axiomatic
specifications of memory models based on empirically observed behavior of
certain ``litmus
tests''\cite{alglave2012formal,Alglave:TACAS,alglave2014herding,Alglave:FMSD,Alglave:2010,Alglave11}.
There has been some work in providing operational and axiomatic semantics that
describes the observed behavior (based on certain ``litmus tests'' of real
hardware
\cite{mador2012axiomatic,sarkar2011understanding,sarkar2012synchronising}.
Finally, there has been work formally relating the axiomatic specification of
TSO to operational semantics \cite{x86tsocacm10}.

>>>>

There has been a lot of work in providing frameworks for axiomatic
specifications of memory models based on empirically observed behavior of
certain ``litmus
tests''\cite{Alglave11,Alglave:FMSD,alglave2012formal,Alglave:2010,Alglave:TACAS,alglave2014herding}.
There has been some work in providing operational and axiomatic semantics that
describes the observed behavior (based on certain ``litmus tests'' of real
hardware
\cite{mador2012axiomatic,sarkar2011understanding,sarkar2012synchronising}.
Finally, there has been work formally relating the axiomatic specification of
TSO to operational semantics \cite{x86tsocacm10}.
